Online Multiclass Linear Classification with Bandit Feedback

### 2018-11-29 arxiv-version/main.tex
Proof of one of the polynomial approximation theorems

We construct several different mappings $\phi$. The mappings differ in the
parameters $R'$, $\gamma'$, time complexity of evaluating $\phi(x)$, and time
complexity of evaluating $k(x,x')$. Some of the mappings depend the original
margin $\gamma$. In practice, the margin parameter $\gamma$ is not known, which
makes these mappings impractical. However, one of the mappings we construct
does \emph{not} depend $\gamma$.

@@

Before we state the theorems, recall that a polynomial of $d$ variables is a
function $p:\R^d \to \R$ of the form
$$
p(x) = p(x_1, x_2, \dots, x_d) = \sum_{i_1, i_2, \dots, i_d} c_{i_1, i_2, \dots, i_d} x_1^{i_1} x_2^{i_2} \dots x_d^{i_d}
$$
where the sum ranges over a finite set of $d$-tuples $(i_1, i_2, \dots, i_d)$ of
non-negative integers and $c_{i_1, i_2, \dots, i_d}$ is a real coefficient. The
\emph{degree} of a polynomial $p$, denoted by $\deg(p)$, is the largest value of
$i_1 + i_2 + \dots + i_d$ for which the coefficient is non-zero. The \emph{norm
of a polynomial} $p$ is defined as
$$
\norm{p} = \sqrt{\sum_{i_1, i_2, \dots, i_d} \left(c_{i_1, i_2, \dots, i_d} \right)^2 } \; .
$$
It is not hard to see that this indeed a norm, since we can interpret it as
a Euclidean norm of the vector of the coefficients of the polynomial.

\begin{theorem}[Polynomial approximation of intersection of halfspaces I]
\label{theorem:polynomial-approximation-1}
Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1}, \norm{v_2}, \dots, \norm{v_m} \le 1$.
Let $\gamma > 0$. There exists a polynomial $p:\R^d \to \R$ such that
\begin{enumerate}
\item $p(x) \ge 1$ for all $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
\item $p(x) \le -1$ for all $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
\item $\deg(p) \le ???$
\item $\norm{p} \le ???$
\item $|p(x)| \le ???$ for all $x \in \R^d$ such that $\norm{x} \le 1$
\end{enumerate}
\end{theorem}

\begin{theorem}[Polynomial approximation of intersection of halfspaces II]
\label{theorem:polynomial-approximation-2}
Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1}, \norm{v_2}, \dots, \norm{v_m} \le 1$.
Let $\gamma > 0$. There exists a polynomial $p:\R^d \to \R$ such that
\begin{enumerate}
\item $p(x) \ge 1/2$ for all $x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
\item $p(x) \le -1/2$ for all $x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
\item $\deg(p) \le ???$
\item $\norm{p} \le ???$
\item $|p(x)| \le ???$ for all $x \in \R^d$ such that $\norm{x} \le 1$
\end{enumerate}
\end{theorem}

The proofs of the theorems can be found in
Sections~\ref{section:proof-of-polynomial-approximation-1}~and~\ref{section:proof-of-polynomial-approximation-2}
respectively.

\section{Proof of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}}

@@

\begin{proposition}[Properties of the norm of polynomials]
\hspace{1cm} % Dummy space
\begin{enumerate}
\item Let $p_1, p_2, \dots, p_n$ be multivariate polynomials and
let $p(x) = \prod_{j=1}^n p_j(x)$ be their product. Then, $\norm{p}^2 \le n^{\sum_{j=1}^n \deg(p_j)} \prod_{j=1}^n \norm{p_j}^2$.
\item Let $q$ be a multivariate polynomial of degree at most $s$ and let $p(x) = (q(x))^n$. Then, $\norm{p}^2 \le n^{ns} \norm{q}^{2n}$.
\item Let be $p_1, p_2, \dots, p_n$ be multivariate polynomials. Then, $\norm{\sum_{j=1}^n p_j}^2 \le n \sum_{j=1}^n \norm{p_j}^2$.
\end{enumerate}
\end{proposition}

\begin{proof}
Using multi-index notation we can write any multivariate polynomial $p$ as
$$
p(x) = \sum_A c_A x^A
$$
where $A = (i_1, i_2, \dots, i_d)$ is a multi-index (i.e. a $d$-tuple of
non-negative integers), $x^A = x_1^{i_1} x_2^{i_2} \dots x_d^{i_d}$ is a
monomial and $c_A = c_{i_1, i_2, \dots, i_d}$ is the corresponding real
coefficient. The sum is over a finite subset of $d$-tuples of non-negative
integers. Using this notation, the norm of a polynomial $p$ can be written as
$$
\norm{p} = \sqrt{\sum_A (c_A)^2} \; .
$$
For a multi-index $A = (i_1, i_2, \dots, i_d)$ we define its $1$-norm as
$\norm{A}_1 = i_1 + i_2 + \dots + i_d$.

To prove the first part, we express $p_j$ as
$$
p_j(x) = \sum_{A_j} c^{(j)}_{A_j} x^{A_j} \; .
$$
If $p$ has expansion $p(x) = \sum_A c_A x^A$ then its coefficient $c_A$ for any multi-index $A$ is
$$
c_A = \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \; .
$$
Therefore,
\begin{multline*}
\norm{p}^2
= \sum_{A} (c_A)^2
= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \right)^2
= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
\end{multline*}
and
\begin{multline*}
\prod_{i=1}^n \norm{p_i}^2
= \prod_{i=1}^n \left( \sum_{A_i} (c^{(i)}_{A_i})^2 \right)
= \sum_{(A_1, A_2, \dots, A_n)} \prod_{j=1}^n (c^{(j)}_{A_j})^2
= \sum_{(A_1, A_2, \dots, A_n)} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \\
= \sum_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
\end{multline*}
where in both cases the outer sum is over multi-indices $A$ such that $\norm{A}_1 \le \deg(p)$.
\autoref{lemma:simple-inequality} implies that for any multi-index $A$,
$$
\left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
\le M_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \; .
$$
where $M_A$ is the number of $n$-tuples $(A_1, A_2, \dots, A_n)$ such that $A_1 +
A_2 + \dots + A_n = A$.

To finish the proof, it is sufficient to prove that
$M_A \le n^{\deg(p)}$. To prove this inequality, consider a multi-index
$A = (i_1, i_2, \dots, i_d)$ and consider its $\ell$-th coordinate $i_\ell$.
In order for $A_1 + A_2 + \dots + A_n = A$, the $\ell$-th coordinates of
$A_1, A_2, \dots, A_n$ need to sum to $i_\ell$. There are exactly $\binom{i_\ell + n - 1}{i_\ell}$
possibilities for the choice of $\ell$-th coordinates of $A_1, A_2, \dots, A_n$.
The total number of choices is thus
$$
M_A = \prod_{\ell=1}^d \binom{i_\ell + n - 1}{i_\ell} \; .
$$
Using \autoref{lemma:binomial-bound}, we upper bound it as
$$
M_A \le \prod_{\ell=1}^d n^{i_\ell} = n^{\norm{A}_1} \le n^{\deg(p)} \; .
$$

@@

\begin{proposition}[Properties of Chebyshev polynomials]
\label{proposition:properties-of-chebyshev-polynomials}
Chebyshev polynomials satisfy
\begin{enumerate}
\item $\deg(T_n) = n$ for all $n \ge 0$.
\item If $n \ge 1$, the leading coefficient of $T_n(z)$ is $2^{n-1}$.
\item $T_n(\cos(\theta)) = \cos(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
\item $T_n(\cosh(\theta)) = \cosh(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
\item $|T_n(z)| \le 1$ for all $z \in [-1,1]$ and all $n \ge 0$.
\item $T_n(z) \ge 1 + n^2(z - 1)$ for all $z \ge 1$ and all $n \ge 0$.
\item All coefficients of $T_n(z)$ lie in the interval $\left[-(1+\sqrt{2})^n, (1+\sqrt{2})^n \right]$.
\end{enumerate}
\end{proposition}

@@

To verify the seventh property let $a_n$ be the magnitude of the largest
coefficient of $T_n(z)$. The recurrence for Chebyshev polynomials implies that
the sequence $a_0, a_1, a_2, \dots$ satisfies
\begin{align*}
a_0 & = a_1 = 1 \; , \\
a_{n+1} & \le 2 a_n + a_{n-1} & \text{for $n \ge 1$.}
\end{align*}
It remains to show that $a_n \le (1 + \sqrt{2})^n$ for all $n \ge 0$. We do this
by induction on $n$. For $n=0$ and $n=1$ the inequality trivially holds. For $n
\ge 1$, we have
\begin{align*}
a_{n+1} \le 2 a_n + a_{n-1}
& \le 2 (1 + \sqrt{2})^n + (1 + \sqrt{2})^{n-1} \\
& = (1 + \sqrt{2})^{n-1} (2 (1 + \sqrt{2}) + 1) \\
& = (1 + \sqrt{2})^{n-1} (3 + 2\sqrt{2}) \\
& = (1 + \sqrt{2})^{n-1} (1 + \sqrt{2})^2 \\
& = (1 + \sqrt{2})^{n+1} \; .
\end{align*}

@@

\subsection{Rational Kernel}
TODO

>>>>

We construct several different mappings $\phi$. The mappings differ in the
parameters $R'$, $\gamma'$, time complexity of evaluating $\phi(x)$, and time
complexity of evaluating $k(x,x')$. Some of the mappings depend the original
margin $\gamma$. In practice, the margin parameter $\gamma$ is not known, which
makes these mappings impractical. However, one of the mappings we construct
does \emph{not} depend on $\gamma$.

@@

Before we state the theorems, recall that a polynomial of $d$ variables is a
function $p:\R^d \to \R$ of the form
$$
p(x) = p(x_1, x_2, \dots, x_d) = \sum_{\alpha_1, \alpha_2, \dots, \alpha_d} c_{\alpha_1, \alpha_2, \dots, \alpha_d} x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}
$$
where the sum ranges over a finite set of $d$-tuples $(\alpha_1, \alpha_2,
\dots, \alpha_d)$ of non-negative integers and $c_{\alpha_1, \alpha_2, \dots,
\alpha_d}$ is a real coefficient. The \emph{degree} of a polynomial $p$, denoted
by $\deg(p)$, is the largest value of $\alpha_1 + \alpha_2 + \dots + \alpha_d$
for which the coefficient $c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is non-zero.
The \emph{norm of a polynomial} $p$ is defined as
$$
\norm{p} = \sqrt{\sum_{\alpha_1, \alpha_2, \dots, \alpha_d} \left(c_{\alpha_1, \alpha_2, \dots, \alpha_d} \right)^2 } \; .
$$
It is easy see that this is indeed a norm, since we can interpret it as a
Euclidean norm of the vector of the coefficients of the polynomial.

\begin{theorem}[Polynomial approximation of intersection of halfspaces I]
\label{theorem:polynomial-approximation-1}
Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma > 0$. There exists a
multivariate polynomial $p:\R^d \to \R$ such that
\begin{enumerate}
\item $p(x) \ge 1$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
\item $p(x) \le -1$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
\item $\deg(p) \le ???$
\item $\norm{p} \le ???$
\end{enumerate}
\end{theorem}

\begin{theorem}[Polynomial approximation of intersection of halfspaces II]
\label{theorem:polynomial-approximation-2}
Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma > 0$. There exists a
multivariate polynomial $p:\R^d \to \R$ such that
\begin{enumerate}
\item $p(x) \ge 1/2$ for all $\displaystyle x \in \bigcap_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \ge \gamma \right\}$
\item $p(x) \le -1/2$ for all $\displaystyle x \in \bigcup_{i=1}^m \left\{ x \in \R^d ~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$
\item $\displaystyle \deg(p) = \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$
\item $\displaystyle \norm{p} \le \left( 188 \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil \right)^{\frac{1}{2} \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil}$
\end{enumerate}
\end{theorem}

The proofs of the theorems can be found in
Section~\ref{section:proof-of-polynomial-approximation}.

TODO: Mappings and kernels!

\section{Proof of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}}
\label{section:proof-of-polynomial-approximation}.

@@

\begin{lemma}[Properties of the norm of polynomials]
\label{lemma:properties-of-norm-of-polynomials}
\hspace{1cm} % Dummy space
\begin{enumerate}
\item Let $p_1, p_2, \dots, p_n$ be multivariate polynomials and let $p(x) =
\prod_{j=1}^n p_j(x)$ be their product.  Then, $\norm{p}^2 \le n^{\sum_{j=1}^n
\deg(p_j)} \prod_{j=1}^n \norm{p_j}^2$.

\item Let $q$ be a multivariate polynomial of degree at most $s$ and let $p(x) =
(q(x))^n$. Then, $\norm{p}^2 \le n^{ns} \norm{q}^{2n}$.

\item Let be $p_1, p_2, \dots, p_n$ be multivariate polynomials. Then,
$\norm{\sum_{j=1}^n p_j}^2 \le n \sum_{j=1}^n \norm{p_j}^2$.
\end{enumerate}
\end{lemma}

\begin{proof}
Using multi-index notation we can write any multivariate polynomial $p$ as
$$
p(x) = \sum_A c_A x^A
$$
where $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ is a multi-index (i.e. a $d$-tuple of
non-negative integers), $x^A = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d}$ is a
monomial and $c_A = c_{\alpha_1, \alpha_2, \dots, \alpha_d}$ is the corresponding real
coefficient. The sum is over a finite subset of $d$-tuples of non-negative
integers. Using this notation, the norm of a polynomial $p$ can be written as
$$
\norm{p} = \sqrt{\sum_A (c_A)^2} \; .
$$
For a multi-index $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ we define its
$1$-norm as $\norm{A}_1 = \alpha_1 + \alpha_2 + \dots + \alpha_d$.

To prove the first part, we express $p_j$ as
$$
p_j(x) = \sum_{A_j} c^{(j)}_{A_j} x^{A_j} \; .
$$
Since $p(x) = \prod_{i=1}^n p_j(x)$, the coefficients of its expansion $p(x) =
\sum_A c_A x^A$ are
$$
c_A = \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \; .
$$
Therefore,
\begin{multline*}
\norm{p}^2
= \sum_{A} (c_A)^2
= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \right)^2
= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
\end{multline*}
and
\begin{multline*}
\prod_{i=1}^n \norm{p_i}^2
= \prod_{i=1}^n \left( \sum_{A_i} (c^{(i)}_{A_i})^2 \right)
= \sum_{(A_1, A_2, \dots, A_n)} \prod_{j=1}^n (c^{(j)}_{A_j})^2
= \sum_{(A_1, A_2, \dots, A_n)} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \\
= \sum_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
\end{multline*}
where in both cases the outer sum is over multi-indices $A$ such that $\norm{A}_1 \le \deg(p)$.
\autoref{lemma:simple-inequality} implies that for any multi-index $A$,
$$
\left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
\le M_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \; .
$$
where $M_A$ is the number of $n$-tuples $(A_1, A_2, \dots, A_n)$ such that $A_1 +
A_2 + \dots + A_n = A$.

To finish the proof, it is sufficient to prove that $M_A \le n^{\deg(p)}$ for
any $A$ such that $\norm{A}_1 \le \deg(p)$. To prove this inequality, consider a
multi-index $A = (\alpha_1, \alpha_2, \dots, \alpha_d)$ and consider its $i$-th coordinate
$\alpha_i$. In order for $A_1 + A_2 + \dots + A_n = A$ to hold, the $i$-th
coordinates of $A_1, A_2, \dots, A_n$ need to sum to $\alpha_i$. There are exactly
$\binom{\alpha_i + n - 1}{\alpha_i}$ possibilities for the choice of $i$-th
coordinates of $A_1, A_2, \dots, A_n$. The total number of choices is thus
$$
M_A = \prod_{i=1}^d \binom{\alpha_i + n - 1}{\alpha_i} \; .
$$
Using \autoref{lemma:binomial-bound}, we upper bound it as
$$
M_A \le \prod_{i=1}^d n^{\alpha_i} = n^{\norm{A}_1} \le n^{\deg(p)} \; .
$$

@@

\begin{proposition}[Properties of Chebyshev polynomials]
\label{proposition:properties-of-chebyshev-polynomials}
Chebyshev polynomials satisfy
\begin{enumerate}
\item $\deg(T_n) = n$ for all $n \ge 0$.
\item If $n \ge 1$, the leading coefficient of $T_n(z)$ is $2^{n-1}$.
\item $T_n(\cos(\theta)) = \cos(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
\item $T_n(\cosh(\theta)) = \cosh(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
\item $|T_n(z)| \le 1$ for all $z \in [-1,1]$ and all $n \ge 0$.
\item $T_n(z) \ge 1 + n^2(z - 1)$ for all $z \ge 1$ and all $n \ge 0$.
\item $\norm{T_n} \le (1+\sqrt{2})^n$ for all $n \ge 0$
\end{enumerate}
\end{proposition}

@@

We verify the seventh property by induction on $n$.
For $n=0$ and $n=1$ the inequality trivially holds, since $\norm{T_0} = \norm{T_1} = 1$.
For $n \ge 1$, since $T_{n+1}(z) = 2zT_n(z) - T_{n-1}(z)$,
\begin{align*}
\norm{T_{n+1}}
& \le 2 \norm{T_n} + \norm{T_{n-1}} \\
& \le 2 (1 + \sqrt{2})^n + (1 + \sqrt{2})^{n-1} \\
& = (1 + \sqrt{2})^{n-1} (2 (1 + \sqrt{2}) + 1) \\
& = (1 + \sqrt{2})^{n-1} (3 + 2\sqrt{2}) \\
& = (1 + \sqrt{2})^{n-1} (1 + \sqrt{2})^2 \\
& = (1 + \sqrt{2})^{n+1} \; .
\end{align*}

@@

To verify the first property notice that if $x \in \R^d$ satisfies $\norm{x} \le
1$ and $\ip{v_i}{x} \ge \gamma$ then since $\norm{v_i} \le 1$ we have
$\ip{v_i}{x} \in [0,1]$. Thus, $T_s(1 - \ip{v_i}{x})$ and $\left( T_s(1 -
\ip{v_i}{x}) \right)^r$ lie in the interval $[-1,1]$. Therefore,
$$
p(x) \ge m + \frac{1}{2} - m \ge \frac{1}{2} \; .
$$

To verify the second property consider any $x \in \bigcup_{i=1}^m \left\{ x \in \R^d
~:~ \norm{x} \le 1, \ \ip{v_i}{x} \le - \gamma \right\}$. Clearly, $\norm{x} \le 1$
and there exists at least one $i \in \{1,2,\dots,m\}$ such that $\ip{v_i}{x} \le
- \gamma$. Therefore, $1 - \ip{v_i}{x} \ge 1 + \gamma$ and~\autoref{proposition:properties-of-chebyshev-polynomials} (part 6)
imply that
$$
T_s(1 - \ip{v_i}{x}) \ge 1 + s^2 \gamma \ge 2
$$
and thus
$$
\left( T_s(1 - \ip{v_i}{x}) \right)^r \ge 2^r \ge 2m \; .
$$
On the oter hand for any $j \in \{1,2,\dots,m\}$, we have $\ip{v_j}{x} \in
[-1,1]$ and thus $1 - \ip{v_j}{x}$ lies in the interval $[0,2]$. According to
\autoref{proposition:properties-of-chebyshev-polynomials} (parts 5 and 6), $T_s(1 - \ip{v_j}{x})
\ge -1$. Therefore,
$$
p(x) = m + \frac{1}{2} - \left( T_s(1 - \ip{v_i}{x}) \right)^r - \sum_{\substack{j ~:~  1 \le j \le m \\ j \neq i}} \le m + \frac{1}{2} - 2m + (m - 1) \le - \frac{1}{2} \; .
$$

The third property follows from observation that degree of $p$
is the same as the degree of any one of the terms
$\left( T_s(1 - \ip{v_i}{x}) \right)^r$ which is $r \cdot s$.

To prove the fourth property, we need to upper bound the norm of $p$.
Let $f_i(x) = 1 - \ip{v_i}{x}$, let $g_i(x) = T_s(1 - \ip{v_i}{x})$
and let $h_i(x) = (T_s(1 - \ip{v_i}{x}))^r$. We have
$$
\norm{f_i}^2 = 1 + \norm{v_i}^2 \le 1 + 1 = 2 \; .
$$
Let $T_s(z) = \sum_{j=0}^s c_j z^j$ be the expansion of $s$-th Chebyshev polynomial.
Then,
\begin{align*}
\norm{g_i}^2
& = \norm{ \sum_{j=0}^s c_j (f_i)^j }^2 \\
& \le (s + 1) \sum_{j=0}^s \norm{c_j (f_i)^j}^2 & \text{(by~part 3 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
& = (s + 1) \sum_{j=0}^s (c_j)^2 \norm{(f_i)^j}^2 \\
& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j \norm{f_i}^{2j} & \text{(by~part 2 of \autoref{lemma:properties-of-norm-of-polynomials})} \\
& \le (s + 1) \sum_{j=0}^s (c_j)^2 j^j 2^{2j} \\
& \le (s + 1) s^s 2^{2s} \sum_{j=0}^s (c_j)^2 \\
& = (s + 1) s^s 2^{2s} \norm{T_s}^2 \\
& = (s + 1) s^s 2^{2s} (1 + \sqrt{2})^{2s} & \text{(by~part 7 of \autoref{proposition:properties-of-chebyshev-polynomials})} \\
& = (s + 1) \left(4(1+\sqrt{2})^2 s \right)^s \\
& \le \left(8(1+\sqrt{2})^2 s \right)^s & \text{(since $s+1 \le 2^s$ for any integers $s \ge 0$)} \\
& \le \left(47 s \right)^s \; .
\end{align*}
Finally,
\begin{align*}
\norm{p}
& \le m + \frac{1}{2} + \sum_{i=1}^m \norm{(g_i)^r} \\
& = m + \frac{1}{2} + \sum_{i=1}^m \sqrt{\norm{(g_i)^r}^2} \\
& \le m + \frac{1}{2} + \sum_{i=1}^m \sqrt{r^{rs} \norm{g_i}^{2r}} \\
& \le m + \frac{1}{2} + m r^{rs/2} \left(47 s \right)^{rs/2} \\
& = m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \; .
\end{align*}
We can further upper bound the last expression by using that $m \le \frac{1}{2} 2^r$.
Since $r,s \ge 1$,
\begin{align*}
\norm{p}
& \le m + \frac{1}{2} + m \left(47 rs \right)^{rs/2} \\
& \le \frac{1}{2} 2^r + \frac{1}{2} + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
& \le 2^r + \frac{1}{2} 2^r \left(47 rs \right)^{rs/2} \\
& = 2^r \left(1 + \frac{1}{2} \left(47 rs \right)^{rs/2} \right) \\
& = 2^r \left(47 rs \right)^{rs/2} \\
& \le 4^{rs/2} \left(47 rs \right)^{rs/2} \\
& \le \left(188 rs \right)^{rs/2} \; .
\end{align*}
Substituting for $r$ and $s$ finishes the proof.
